Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-20 WSSSPE1_report/WSSSPE1_summary_report.tex
concl on sec 8

Finally, it appears that the career options of developers from different kinds
of software projects differ significantly. In order to further investigate the
much discussed issue of career paths for developers of these software, we
conducted a small survey of the use-cases discussed above with respect to the
current status of its core developers. We looked at the workshop submissions
and the original cited papers for the respective software. Where available, we
looked at the web pages and source code of the earliest versions to find the
original developers. We included projects older than 5 years and excluded
relatively new projects such as \toolname{SciPy} and \toolname{numFOCUS} from
this survey. we find that in a majority of scientific software more than one
original developers are still around, in some cases for more than 10 years,
(eg. \toolname{R/qtl}).  Whereas, in the case of utility software projects, it
appears that at least one original developer is still around, often in a
part-time or ``benefactor'' role. In other cases, it appears that the original
developers have went on to assume a larger role, with the same project.

@@

>>>>

Finally, it appears that the career options of developers from different kinds
of software projects differ significantly. In order to further investigate the
much discussed issue of career paths for developers of these software, we
conducted a small survey of the cases discussed above with respect to the
current status of its core developers. We looked at the workshop submissions
and the original cited papers for the respective software. Where available, we
looked at the web pages and source code of the earliest versions to find the
original developers. We included projects older than 5 years and excluded
relatively new projects such as \toolname{SciPy} and \toolname{numFOCUS} from
this survey. We find that in a majority of scientific software, more than one
original developer are still around, in some cases after more than 10 years,
(eg. \toolname{R/qtl}).  Whereas, in the case of utility software projects, it
appears that at least one original developer is still around, often in a
part-time or ``benefactor'' role. In other cases, it appears that the original
developers have went on to assume a larger role, with the same project.

@@

% Conclusion of S8 : Use Cases, not sure where to put
\note{conclusions from S8, not sure of location --Ketan}

Two distinct class of scientific software projects and products were discussed
in the workshop: 1) generic, large-scale utility software and 2) niche, medium-
and small-scale scientific software. Each class faces different and significant
challenges. New undertakings should recognize the differences in advance and
identify such challenges within the development and sustaining efforts. In
particular, the dynamics associated with developers, scope, life cycle,
users-community, (re)usability, funding support and career paths vary widely
among the two classes of software.

% end conclusion S8
